HO unification from object language to meta language

### 2024-04-01 paper/main.tex
begin 6.3

@@

>>>>

TODO: W preservation \cref{prop:nf}

@@

\newcommand{\progressetaleft}{\emph{progress-$\eta$-left}}
\begin{definition}[\progressetaleft]\label{def:progressetaleft}
A link \linketaM{\Gamma}{X}{T} is removed from \linkStore when
$X$ becomes rigid. There are two cases:
\begin{enumerate}
  \item if $X = a$ or $X = f \appsep a_1\ldots a_n$
    we unify the $\eta$-expansion of the $X$ with $T$, that is we run
    $\lambda x.X \appsep x\Ue{} T$  (under
    the context $\Gamma$)
  \item if $X = \lambda x.t$ we run $X \Ue{} T$.
\end{enumerate}
\end{definition}

\newcommand{\progressetaright}{\emph{progress-$\eta$-right}}
\begin{definition}[\progressetaright]\label{def:progressetaright}
A link \linketaM{\Gamma}{X}{T} is removed from \linkStore when
$\testmaybeeta{} T$ does not hold (anymore) and by $\eta$-contracting
$T$ to $T'$ (if possible, else $T' = T$) and executing $X \Ue{} T'$ (under
the context $\Gamma$).
\end{definition}

There is a third case in which a link is removed from \linkStore, namely
when the \lhs is assigned to another variable that is the \lhs of another
\linketa.

\newcommand{\progressetadedup}{\emph{progress-$\eta$-deduplicate}}
\begin{definition}[\progressetadedup]\label{def:progressetadedup}
  A link \linketaM{\Gamma}{X_{\vec{s}}}{T} is removed from \linkStore when
  another link \linketaM{\Delta}{X_{\vec{r}}}{T'} is in  \linkStore.
  By \cref{inv:uvaarity} the length of $\vec{s}$ and $\vec{r}$ is the same
  hence we can move the term $T'$ from $\Delta$ to $\Gamma$ by renaming its
  bound variables, i.e. $T'' = T[\vec{r}/\vec{s}]$.
  We then run $X_S \Ue{} T''$ (under the context $\Gamma$).
\end{definition}
